Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-03-21 latex/comp_or.tex
Paper update

		{\bf This work}             & $\bigstar$ & $\bigstar$  &$\bigstar$ &$\bigstar$&$\bigstar$& $.$      & $.$      & $\bigstar$ & $\bigstar$&  $.$       &  $\bigstar$  \\
		\bottomrule 
	\end{tabular}
	\normalsize 
\end{table}

@@

In this work, we raise three hypotheses for improvements to the work of \cite{MesquitaSanches2023}:
(1) Computer parallelism could improve {\it Shims}'s performance.
(2) The {\it Shims}' results may have been inferior to that; it could be that a sequential approach to pallet building may lead to a premature stop due to the torque constraints.
(3) The distances to move pallets on unloading in the next node could be minimized to benefit unloading costs.

So, this work seeks to improve their results in terms of quality and performance by using computer parallelism, CG balancing between {\it Shims}' phases, and minimizing the distance between the next node-destined pallets and the cargo door.

These improvements in their heuristics are meant to reduce the stress that transport planners are subjected to, because they have to deal with a lot of information in planning the aircraft route, assembling the pallets, and picking up and delivering at each node. To the best of our knowledge, that is the first time that an air cargo transport problem that simultaneously involves APP, WBP, PDP and TSP has been addressed, and the first time ACLP+RPDP is solved with computer parallelism.

@@

	\item At each node of the flight plan, the items to be allocated are characterized by weight, volume, scores, and previously known destinations, but do not have dimensions. We leave the consideration of 2D or 3D items for future work.

	\item We also disregarded {\it hazardous} items, which eventually could be treated as high score items and other specific constraints.

@@

\bgroup
\def\arraystretch{1.2}
\begin{table}[H]
	\centering
	\small
	\begin{tabular}{MT}
		&Informally, ACLP+RPDP can be summarized as follows:\\
		\midrule
		max &  (items score sum) / (tour cost) of picked up and delivered items on a tour  \\
		\midrule
s.t.    & Along a tour, the set of unvisited nodes is updated. \\
		& In each node, an item may be included in at most one pallet.\\		
		& In each node, consolidated items are composed of items with the same destination. \\
		& Weight, volume and score of a consolidated item are the corresponding sum of their components.\\
		& Consolidated items remain on board until their destinations.\\	
		& Consolidated items can only be included in the same pallet if their destinations are the same.\\
		& Only items destined for the remaining nodes can be loaded.  \\
		& The lateral and longitudinal torques must be within the operational range of the aircraft.\\
		& Weight and volume limitations of pallets must be respected.\\
		& The total weight must be less than the aircraft payload or the total pallet capacity, whichever is the lowest.\\	
		& {\bf The pallets destined for the next node of the tour should be put as near as possible to the cargo ramp door (our inclusion)}.\\		
		\midrule
	\end{tabular}
	\normalsize
\end{table}
\egroup

@@

{\color{blue} \State	$G_3 \gets minRampDist(G_2)$  \label{tour:minRampDist} }

			\State $s, \epsilon \gets ScoreAndDeviation(\pi(k), G_3)$ \label{tour:analyse}
			\State $score \gets score + s$ \label{tour:score2}
			\State $cost \gets cost + c_{\pi(k),\pi(k+1)} * (1 + c_g * |\epsilon|)$ \label{tour:cost2} 
		\EndFor  \label{tour:loop2}
		\Return $score / cost$ \label{tour:f}

@@

		\State Let $G(M,\ Q_{\pi(k)},\ E_{\pi(k)})$ \label{mpShims:g1} \Comment{the initial solution solution}

@@

@@

In this work, we raised three hypotheses for improvements to the work of \cite{MesquitaSanches2023}:

@@

@@

We converted \cite{MesquitaSanches2023} {\it Shims} into a process-based parallel computing heuristic, which we called {\it Multiprocessing Shims} or {\it mpShims}, that quickly finds good solutions for a wide range of problem sizes, our first contribution.

@@

Other important contributions are that we checked three hypotheses: Computer parallelism improved {\it Shims} performance; the intermediate integer programming procedure added to {\it Shims} algorithm enhanced it's results; but the integer programming procedure to minimize pallets' travel in the cargo bay did not improve the results.

>>>>

		{\bf This work}             & $\bigstar$ & $\bigstar$  &$\bigstar$ &$\bigstar$&$\bigstar$& $.$      & $\bigstar$      & $\bigstar$ & $\bigstar$&  $.$       &  $\bigstar$  \\
		\bottomrule 
	\end{tabular}
	\normalsize 
\end{table}

@@

In this work, we raise four hypotheses for improvements to the work of \cite{MesquitaSanches2023}:
(1) Computer parallelism could improve {\it Shims}'s performance.
(2) The {\it Shims}' results may have been inferior to that; it could be that a sequential approach to pallet building may lead to a premature stop due to the torque constraints.
(3) The distances to move pallets on unloading in the next node could be minimized to benefit ground handling costs.
(4) A post-optimization procedure for 3D packing running in parallel mode would keep the run time adequate for operational use.

So, this work seeks to improve their results in terms of quality and performance by using computer parallelism, CG balancing between {\it Shims}' phases, minimizing the distance between the next node-destined pallets and the cargo door, and performing a 3D packing procedure on each pallet.

These improvements in their heuristics are meant to reduce the stress that transport planners are subjected to, because they have to deal with a lot of information in planning the aircraft route, assembling the pallets, and picking up and delivering at each node. To the best of our knowledge, that is the first time that an air cargo transport problem that simultaneously involves APP, WBP, PDP, TSP, and 3D packing has been addressed, and the first time ACLP+RPDP is solved with computer parallelism.

@@

	\item We disregarded {\it hazardous} items, which eventually could be treated as high score items and other specific constraints.

@@

\bgroup
\def\arraystretch{1.2}
\begin{table}[H]
	\centering
	\small
	\begin{tabular}{MT}
		&Informally, ACLP+RPDP can be summarized as follows:\\
		\midrule
		max &  (items score sum) / (tour cost) of picked up and delivered items on a tour  \\
		\midrule
s.t.    & Along a tour, the set of unvisited nodes is updated. \\
		& In each node, an item may be included in at most one pallet.\\		
		& In each node, consolidated items are composed of items with the same destination. \\
		& Weight, volume and score of a consolidated item are the corresponding sum of their components.\\
		& Consolidated items remain on board until their destinations.\\	
		& Consolidated items can only be included in the same pallet if their destinations are the same.\\
		& Only items destined for the remaining nodes can be loaded.  \\
		& The lateral and longitudinal torques must be within the operational range of the aircraft.\\
		& Weight and volume limitations of pallets must be respected.\\
		& The total weight must be less than the aircraft payload or the total pallet capacity, whichever is the lowest.\\	
		& {\bf The pallets destined for the next node of the tour should be put as near as possible to the cargo ramp door (our inclusion)}.\\
		& {\bf The items allocated to each pallet should be submitted to a 3D packing procedure (our inclusion)}.\\				
		\midrule
	\end{tabular}
	\normalsize
\end{table}
\egroup

@@

{\color{blue}   \State	$G_3 \gets minRampDist(G_2)$  \label{tour:minRampDist} }
{\color{purple} \State	$G_4 \gets 3Dpacking(G_3)$  \label{tour:3dpacking} }

			\State $s, \epsilon \gets ScoreAndDeviation(\pi(k), G_4)$ \label{tour:analyse}
			\State $score \gets score + s$ \label{tour:score2}
			\State $cost \gets cost + c_{\pi(k),\pi(k+1)} * (1 + c_g * |\epsilon|)$ \label{tour:cost2} 
		\EndFor  \label{tour:loop2}
		\Return $score / cost$ \label{tour:f}

@@

		\State Let $G(M,\ Q_{\pi(k)},\ E_{\pi(k)})$ \label{mpShims:g1} \Comment{the initial solution}

@@

\subsection{3D packing}

We implemented a post-optimization procedure for three-dimensional (3D) packing according to the instructions on \cite{DubeKanavathy2006} and on \cite{PaquayLimbourgSchynsOliveira2018}, to pack the items selected for each pallet.

Our implementation was also based on \cite{RuizRibeiro}, taking advantage of the already implemented Python classes and auxiliary procedures.

The heuristic solutions consider that, theoretically, all items selected for the pallets would fit on that pallet. But, due to the variability in item dimensions, an actual fit is not possible, causing some unfit items to be excluded from the previous heuristic's solutions (line \ref{3dpacking:unfit}).

Another important contribution is that we implemented parallel 3D packing with each pallet as a process.

\begin{algorithm}[H]
	\caption{Parallel 3D packing procedure}  \label{alg:3dpacking}

		\Procedure{$3Dpacking$}{${N_{\pi(k)}, \pi(k)}, limit, G$}

		\State Let $G(M,\ Q_{\pi(k)},\ E_{\pi(k)})$ \label{3dpacking:g1} \Comment{the initial solution}

		\For{$i \gets 1$ to $m$}
		\State $proc_i \gets 3Dpacker(p_i,\ N_{\pi(k)},\ \pi(k),\ G )$   \label{3dpacking:greedy}
		\State $proc_i.start$
		\EndFor

		\For{$i \gets 1$ to $m$}
		\State $proc_i.join$   \Comment{wait for the packing process to finish.}
		\State $E_{\pi(k)} \gets E_{\pi(k)} \setminus proc_i.unfit$  \label{3dpacking:unfit} \Comment{exclude the unfit item from solution}
		\EndFor

		\Return $G(M,\ N_{\pi(k)} \cup Q_{\pi(k)},\ E_{\pi(k)})$ \label{3dpacking:return}

@@

In this work, we raised four hypotheses for improvements to the work of \cite{MesquitaSanches2023}:

@@

(4) The post-optimization procedure for 3-D packing generated an unfit item percentage of approximately 20\%. This solution phase was a parallel 3-D packing with each pallet as a process, which decreased this phase's run time by an $n$ factor where $n$ is the number of pallets. This was possible because each packing process is completely independent; there is no multiprocessing shared memory. It is also important to highlight that, after the items were excluded, the CG deviation was kept within its operational and feasible range.

@@

We converted {\it Shims} into a process-based parallel computing heuristic, which we called {\it Multiprocessing Shims} or {\it mpShims}, that quickly finds good solutions for a wide range of problem sizes, our first contribution.

@@

Other important contributions are that we checked four hypotheses: Computer parallelism improved {\it Shims} performance; the intermediate integer programming procedure added to {\it Shims} algorithm enhanced it's results; but the integer programming procedure to minimize pallets' travel in the cargo bay did not improve the results; and a post-optimization procedure for 3-D packing was turned possible for operational use due to a process-based parallel computing heuristic.
